---
title: "Communism and Capitalism Analysis"
output: html_notebook
---
Install and load necessary packages. 
 
```{r, message=FALSE, warning=FALSE}
packages.used=c("rvest", "tibble", "qdap", 
                "sentimentr", "ggplot2", "dplyr",
                "tm", "syuzhet", "factoextra", 
                "beeswarm", "scales", "RColorBrewer",
                "RANN", "tm", "topicmodels","readtext")

packages.needed=setdiff(packages.used, 
                        intersect(installed.packages()[,1], 
                                  packages.used))

if(length(packages.needed)>0){
  install.packages(packages.needed, dependencies = TRUE)
}


library("rvest")
library("tibble")
library("qdap")
library("sentimentr")
library("ggplot2")
library("dplyr")
library("tm")
library("syuzhet")
library("factoextra")
library("beeswarm")
library("scales")
library("RColorBrewer")
library("RANN")
library("tm")
library("topicmodels")
library("readtext")

```
Import data
```{r}
ph <- read.csv("../data/philosophy_data.csv", header = TRUE)
cm <- ph[ph$school = "communism"]
cp <-  ph[ph$school = "capitalism"]
cm <- cm.head(2000)
cp <- cp.head(2000)
```

#Topic modeling 

Converted capitalism sentences into a corpus
```{r}
cp_topics <- Corpus(VectorSource(cp$sentence_lowered))

cp_topics<-tm_map(cp_topics, removeNumbers)
cp_topics<-tm_map(cp_topics, removeWords, stopwords("english"))
cp_topics<-tm_map(cp_topics, removeWords, c("the", "may", "one", "must", "can", "will", "two", "upon", "great", "part", "always", "therefore", "much"))
cp_topics <-tm_map(cp_topics, removePunctuation)
cp_topics <-tm_map(cp_topics, stripWhitespace)
```

Document-term matrix is used to create a model with 5 topics with terms that are most probable for each topic
```{r}
cp.dtm <-DocumentTermMatrix(cp_topics)

rowTotals <- apply(cp.dtm , 1, sum)
cp.newdtm  <-cp.dtm[rowTotals> 0, ] 
cp_lda<-LDA(cp.newdtm, k=5,control=list(seed=1234))
```

#Terms associated with frequent topics within capitalist texts
```{r}
terms(cp_lda, 5) 
```

From the topics, we can gather that that frequent terms repeated within the school of capitalism
are associated with economy with a lot of overlap in terms such as labour or profit

Steps are repeated for communism
```{r}
cm_topics <- Corpus(VectorSource(cm$sentence_lowered))

cm_topics<-tm_map(cm_topics, removeNumbers)
cm_topics<-tm_map(cm_topics, removeWords, stopwords("english"))
cm_topics<-tm_map(cm_topics, removeWords, c("the", "may", "one", "must", "can", "will", "two", "upon","form", "use", "must", "commodities", "value", "therefore"))
cm_topics <-tm_map(cm_topics, removePunctuation)
cm_topics <-tm_map(cm_topics, stripWhitespace)

cm.dtm <-DocumentTermMatrix(cm_topics)
rowTotals <- apply(cm.dtm , 1, sum)
cm.newdtm  <-cm.dtm[rowTotals> 0, ] 
cm_lda<-LDA(cm.newdtm, k=5,control=list(seed=1234))
```

#Topics model for communism
```{r}
terms(cm_lda, 5)
```
From the topics, we can gather that that frequent terms repeated within the school of communism
revolve around currency and commodities


Grouping the terms by topic

```{r}
cp_topics<-tidy(cp_lda, matrix ="beta")

cp_top_terms <- beta_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 5) %>% 
  ungroup() %>%
  arrange(topic, -beta)


cm_topics<-tidy(cm_lda, matrix ="beta")

cm_top_terms <- cm_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 5) %>% 
  ungroup() %>%
  arrange(topic, -beta)

```

#Displaying the grouped terms onto a bar chart
```{r}
cp_top_terms %>%
  mutate(Capitalism = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, Capitalism, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()

cm_top_terms %>%
  mutate(Communism = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, Communism, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()




```

# Sentiment Analysis

```{r}
tidy_cp <- cp$tokenized_txt 
tidy_cp <- tibble(line=1:2000, text=tidy_cp)
tidy_cp <- tidy_cp %>% unnest_tokens(word, text)

tidy_cm <- cm$tokenized_txt 
tidy_cm <- tibble(line=1:2000, text=tidy_cm)
tidy_cm <- tidy_cm %>% unnest_tokens(word, text)

nrc_communism <- tidy_cm%>%
  inner_join(get_sentiments("nrc")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

nrc_capitalism <- tidy_cp%>%
  inner_join(get_sentiments("nrc")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

```

#Visualization
```{r}
nrc_communism %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ggplot(aes(reorder(word, n), n, fill = sentiment)) +
  geom_bar(alpha = 0.8, stat = "identity", show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Communism Sentiments", x = NULL) +
  coord_flip()

nrc_capitalism %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ggplot(aes(reorder(word, n), n, fill = sentiment)) +
  geom_bar(alpha = 0.8, stat = "identity", show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Capitalism Sentiments", x = NULL) +
  coord_flip()

```

Within Communism, negative sentiments and emotioms correlate with materialism and alienation, whereas, Capitalism associates negative emotions with poverty and inferiority as well as positive emotions with economic individualism

